---
title: "model.plot"
author: "Hayley Arader"
output: html_document
---

```{r setup, include=FALSE}
library(model.plot)
```

# Welcome!
Welcome to `model.plot`! `model.plot` is an R package designed to make it easier to plot, interact with, and interpret your basic model results. 

# Installation
```{r, eval = FALSE}
devtools::install_github("harader/model.plot")
libary(model.plot)
```

# Usage
Let's load some data from the ISLR package and play around

```{r, warning = FALSE, results = 'hide'}
library(ISLR)
summary(College)
```

This looks like an interesting data set about colleges! Let's subset to only private colleges, and run a regression on out of state tuition:

```{r, warning = FALSE}
my_model <- lm(Outstate ~ perc.alumni + Grad.Rate + Top10perc + PhD + Terminal, data = College[College$Private == "Yes", ])

# Standard plot
plot(my_model)
```

Cool! Now let's say we want to see all variables, not just where p < .05
```{r, warning = FALSE}
plot(my_model, p = 1)
```

And now a bar plot...
```{r, warning = FALSE}
bar_plot(my_model)
```

And a table...
```{r, warning = FALSE}
stat_table(my_model)
```

Woohoo! Happy Plotting!
